%!TEX root = thesis.tex

\section{Acknowledgements}

\itshape
I would not be where I am today without countless hours of wrong turns and
blind charges.
I have some people to thank for their criticisms at one time or another.
Richard Kelso (2004): "[This] leaves me wondering whether you are just juggling magnets." (Turns out at the time that, yes, I was.)
Paraphrasing Nobua Tanaka (2005): "A spring made with magnets is still a spring!"
Will Robertson (2007): "What have I been doing for the last four years?"
Will Robertson (2011): "Okay, time to actually get to work."
(Inspiration and perspiration was bound to strike eventually.)

My first thanks go to my busy supervisors Ben and Anthony, who gave me the freedom to be myself and have inspired me in ways beyond just my work.
My appreciation for the long leash they allowed me couldn't be greater.
With stricter guidance I may have finished sooner, but I believe neither I nor this thesis would have been the better for it.

My second thanks are for the people I've met and spent time with over the years in association with my studies.
Justin Ghan got me into this whole mess to begin with, and from even the other side of the world I feel like I've strange loops of him in my head.
Rohin Wood and Dick Petersen were great friends and influences in the years we spent together in the office; Zebb Prime has been the best of co-conspirators.
Mike Kidner and I had some great talks and shared many interests; on reflection, working with him kick-started my \PhD/ back in 2006.
Around a similar time, Guillaume Barrault was my brother in arms in the time he spent in Adelaide, from the very first week.
Later, in 2009, Hannah Weisbecker reminded me of my passion for engineering and expanded my culinary world.
And, of course, to Elise Fahy for keeping me young.

My third thanks are for the circles of people I've spent time in life with outside of work, not least my (quite!) various housemates.
Ainslee Dewet-Piper and all the whole gang of people at Chocolate Bean have been a great constant in my life.
My time there was a singular pleasure in my life.

My fourth thanks are for those who I've worked with on projects unrelated to my thesis.
The world is large, but seems much less so when people who've never met collaborate from across the globe on shared passions and distractions.
Frank Mittelbach especially has been a great inspiration for his wisdom and encouraging words.

My final thanks go to all of my family who have shared in this amazing period of my life, particularly those loved ones have come into the world and those loved ones who have left it during this time.
Most of all, for she who's shared my crazy life for as much time as this project, Toni Main: you are my complement and our adventures next will be like nothing that's come before.
\upshape
