\documentclass[11pt,a4paper]{memoir}
\def\asydir{\jobname}
\usepackage{thesis-preamble}
\EndPreamble
\title{
Modelling and design of magnetic levitation systems for vibration isolation
}
\begin{document}

\pagestyle{empty}
\phantomsection
\label{titlepage}
\bookmark[dest=titlepage]{Title page}
\calccentering{\unitlength}
\begin{adjustwidth*}{\unitlength}{-\unitlength}
\setlength{\parindent}{0pt}

\begin{flushright}
  \grf[width=50mm]{Figures/logo}\hspace*{-1cm}
\end{flushright}

\vfill

Faculty of Engineering,
Computer and Mathematical Sciences\\
\textsc{school of mechanical engineering}

\vfill

\begin{minipage}{0.97\textwidth}
\Large\raggedright\csname @title\endcsname
\end{minipage}

\vspace{10mm}

William Samuel Parker Robertson

\vfill
\vfill

\begin{minipage}{0.50\textwidth}
\raggedright
\itshape
A thesis submitted in fulfilment of the\\ requirements for the degree of\\
Doctor of Philosophy

\bigskip
August 2013
\end{minipage}
\vfill

\end{adjustwidth*}

\clearpage

\null\vfill

\begin{center}

\itshape

  \begin{tabular}{@{}l@{~~}l@{}}
  Supervisors:    & Assoc.\,Prof.\ Ben Cazzolato  \\
                  & Assoc.\,Prof.\ Anthony Zander
  \end{tabular}
  
  \bigskip
  
  Copyright %\textcopyright\
  2003--2013 Will Robertson

  \bigskip
  Document generated \today\\
  Submission date: August 9, 2013


  \bigskip
  School of Mechanical Engineering\\
  The University of Adelaide, 5005\\
  SA, Australia
\end{center}

\cleardoublepage

\def\PPP{\unskip~\,\textup\P~\,}

\section*{Colophon}

{\centering\begin{minipage}{0.89\textwidth}
\parfillskip=0pt
This document has been prepared and typeset using \LaTeX{}.
The width of the text block is 369\,pt, and the text is set with the font Palatino at size 11\,pt and leading 13.6\,pt.
Microtypographical features, including margin kerning, have been used to ensure better typesetting.
\PPP
Page margins have been chosen as a trade-off between trying to achieve an optimal number of characters per line for ease of reading~\makebox[\widthof{[50]}]{\cite{bringhurst-typestyle}} and fitting the typeblock well onto \acro{A4} stock.
Due to the large space available in the margins, many figures are typeset intentionally to protrude into them.
\PPP
If you are reading this electronically, \PDF\ hyperlinks have been automatically inserted in all appropriate cross-referencing positions, including the nomenclature and bibliography.\par
\end{minipage}\par}

\cleardoublepage

\section*{Declaration}

{\centering\begin{minipage}{0.89\textwidth}
\nonfrenchspacing
\parfillskip=0pt
I certify that this work contains no material which has been accepted for the award of any other degree or diploma in any university or other tertiary institution and, to the best of my knowledge and belief, contains no material previously published or written by another person, except where due reference has been made in the text. In addition, I certify that no part of this work will, in the future, be used in a submission for any other degree or diploma in any university or other tertiary institution without the prior approval of the University of Adelaide and where applicable, any partner institution responsible for the joint-award of this degree.
\PPP
I give consent to this copy of my thesis, when deposited in the University Library, being made available for loan and photocopying, subject to the provisions of the Copyright Act 1968.
\PPP
I also give permission for the digital version of my thesis to be made available on the web, via the University’s digital research repository, the Library catalogue and also through web search engines, unless permission has been granted by the University to restrict access for a period of time.
\par

\vspace*{1cm}

\hrulefill\hrulefill\hrulefill\hfill\hrulefill\hrulefill

\noindent\small\textsc{signed}\hfill\textsc{dated}

\end{minipage}\par}


\end{document}
