%!TEX root = thesis.tex

\chapter{Introduction}

\epigraph{In my experience I found that the most effective way to express
something in order to make others understand is to use the simplest language.
Also I learned from teaching that the more rigid the language the less
effective it is.}{\textcite{mahathera1990}}

\section{One paragraph summary of the thesis}

Vibration disturbance is a consistent complaint that will always exist to
negatively influence equipment and processes. The theme of this thesis
investigates using permanent magnets in the design of a vibration isolation
mount. Permanent magnets can be used to either support load or to reduce the
fundamental resonance frequency of a system. In the first half of the thesis,
simple permanent magnet arrangements are examined for load bearing, with
multiple designs suitable for a variety of objectives. In this vein,
electromagnetic coil forces and multipole (or Halbach) arrays of magnets are
also investigated. In the second half of the thesis, more attention is paid on
realising these systems for vibration isolation, namely, by reducing the
resonant frequency with stiffness-reducing elements. Usually these
stiffness-reducing elements are permanent magnets in attraction, but
mechanical springs are analysed briefly as well. Some different active control
techniques are investigated for further improvements to the low-frequency
isolating design. An experimental prototype tying together the major concepts
of work is shown last, demonstrating results of an permanent magnet, active,
low-frequency, vibration-isolating apparatus.

\section{Introduction to the central themes of the thesis}

\subsection{The problem of vibrations}

The disturbing effects of vibrations are a well0known and continuing problem.
The transmission of vibrations from a source can only ever be reduced, not eliminated — that is, not without removing the source entirely from the local region affected. And in many cases there is no single source; the very ground itself may be a medium through which undesirable vibrations are transmitted.
Earthquakes are an extreme example of this, but on a smaller scale there are continuous time-varying displacements of the `fixed' ground beneath us.
\note{Not to be too earth-centric, but many of the ideas here a different relevance in off-planet circumstances.}
The earth should in fact be considered as a distributed vibrating structure, of very great mass in total, that has a range of displacement profiles dependent on the local surrounding impedance conditions. 

Mitigating the effects of a disturbance through the base on which a structure is supported is known as `vibration isolation' and is the over-arching problem in which the work of this thesis should be put in context.

A contrasting vibration problem occurs when some manner of machine causes its own vibration; a well-known example is a washing machine tha exerts an oscillating disturbance force on itself through a mass imbalance. This type of vibration problem requires a rather different set of design solutions and often its solution acts in opposition to the vibration isolation problem discussed above. Reducing the effects of self-induced vibration disturbance will be termed `vibration suppression'
\note{The descriptor `Vibration isolation' is commonly used to refer to both problems, but it would be confusing here to avoid the clarification.}
for the purposes of this thesis and will be revisited on occassion herein.

There are a variety of `classic' solutions for both vibration isolation and
vibration suppression. A particularly simple solution for \emph{both} problems is to mount the equipment on a many-ton slab of concrete. This is not always practical. Another common approach for vibration isolation is to support the equipment with pneumatic springs. When in operation, these springs provide a low supporting stiffness and low static deflection; they can typically be used to support hundreds of kilograms with resonance frequency of less than five hertz.

Other support methods besides pneumatics are able to achieve low stiffness; this is an area that will be further investigated in the literature review. But one method in particular is interesting in this context: permanent magnets can provide low stiffness support without energy expenditure. Their nonlinear forces in both attraction and repulsion allows the possibility of interesting supporting designs, and their non-contact nature allows their use in vacuum and `clean-room' environments.

\subsection{Permanent magnets used for mechanical design}

The last twenty years has seen the maturation of the rare earth permanent magnet industry. These magnets are now widely available in large sizes and strong magnetisation at relatively low prices. They are now used in a variety of mechanical design, including bearings, couplings, \maglev\ trains, and so on, which take advantage of non-contact attractive and/or repulsive forces.
Magnets can be used to make other magnets move or to keep them in place — there is little limi to the ingenuity of their application. However, in part to this complex behaviour between them, there are few design guidelines that can be used to aid their use [quote Moskowitz].

We can speak broadly about their integrated use in force design: magnets can be used in conjunction with current-carrying coils to effect time-varying forces (as in shakers and speakers); soft iron can be used to guide the magnetic fields into desired regions or away from unwanted areas (\eg, latches and motors); or magnets can be used alone for unique force--displacement characteristics or simply for applying non-contact forces (\eg, bearings).

These ideas in mechanics and dynamics have application back to the field of vibrations. A `synergy' between the two fields is seen in areas such as energy harvesting from ambient vibration, the study of vibration in high-speed magnetic bearings, and one of the main themes of this thesis — nonlinear and/or noncontact forces for support equipment for vibration isolation.

Support mass with a noncontact force can also be called `levitation', an area which deserves its own mention. \textcite{earnshaw1839} proved that levitation with the force of permanent magnets alone was impossible, although this did not become common knowledge
\note{If it can even be said to be `commonly known' today. Anecdotal evidence suggests otherwise.}
until much later — given by the range of patents issued that assume the opposite. Exceptions to `Earshaw's Theorem' include the use of diamagnetic materials and actively-controlled system, amongst some others. It is the possibility of overcoming instability with active means that is of interest in this thesis.

\subsection{\QZS\ systems}

The transition between stable and unstable forces becomes interesting in the context of vibration isolation. Between positive and negative stiffness in a force--displacement characteristic, there is a inflexion point of zero stiffness. This point is termed a `\qzs' position to emphasise that the dynamic behaviour of the system in this condition can be rather complex and usually unstable. `True' zero stiffness would imply \emph{no} connection between between the mass and the base, as if they were floating in free space — the motion of one would have no effect on the motion of the other.

As systems approach \qzs, their vibration isolation inproves as the resonant frequency decreases. Operation at the \qzs\ position is not possible as the system is, at best, only marginally stable, and the system must be tuned (based on the applied loading) to achieve best results.

Certain magnetic systems are not the only ones to exhibit \qzs. The phenomenon was first proposed using inclined springs to achieve a `buckling' effect. Magnets are more convenient in many ways than inclined or buckling springs in that the negative stiffness can be applied directly without having to exploit the byproduct of a mechanical spring or linkage arrangement, which can be more bulky.

Active control systems can be used with \qzs\ systems to improve their performance in one of three ways:
\begin{enumerate}
  \item Standard active vibration control with velocity feedback;
  \item Remove the instability at the \qzs\ location with a nonlinear controller;
  \item Online tuning of the system for load-independent operation.
\end{enumerate}
The first two of these strategies are investigated in this thesis.

\section{Project exposition}

The purpose of this project is to design and build a vibration
isolation table using non-contact magnetic springs. This goal can be
split into two: the design of a non-contact magnetic spring (suitable
for a vibration isolation table); and the design of the vibration
isolation table itself.

Vibration isolation tables are generally designed to attenuate natural
disturbances from the ground to the tabletop. These are used for
example in optics systems as well as in situations that involve
vibration-sensitive equipment. Current commercial models use pneumatic
springs to perform this task, and this project arose out of curiosity:
could magnetic springs be used instead?

Since the invention of the rare-earth magnet, there have been great
strides in creating wonderful inventions such as the maglev train and
the planar levitator. To date, comparatively little work has been
undertaken on vibration isolation of large loads using predominantly
passive elements. While levitating trains are heavy, they require
little positioning accuracy; meanwhile, planar levitators are
astonishingly accurate, but may only bear small loads. A vibration
isolation table must do both.

Using magnets for load bearing brings its own set of challenges. For
completely non-contact support, active control must be used to
stabilise \emph{at least} one degree of freedom. For the design to be
worth investigating, some advantage to using magnets should also be
demonstrated.\footnote{Although I took much pleasure in explaining
  over the years that my \PhD\ project was to `build a table that
  floats on magnets'.}


\section{Topical applications of magnetic forces}

\textcite{coey2002} discusses a broad range of magnetic applications,
summarised in \tabref{magnet-applications}.

\begin{table}
\begin{tabular}{@{}lll@{}}
\toprule
Field & Magnetic effect & Examples \\
\midrule
Uniform & Zeeman splitting & Magnetic resonance imaging \\
& Torque & Alignment of magnetic powder \\
& Hall effect, magnetoresistance & Sensors, read-heads \\
& Force on conductor & Dynamic Motors, actuators, loudspeakers \\
& Induced emf & Generators, microphones \\
Nonuniform & Force on charged particles & Beam control, 
radiation sources (microwave, uv; X-ray) \\
& Force on magnet & Bearings, couplings, Maglev \\
& Force on paramagnet & Mineral separation \\
Time varying & Varying field & Dynamic Magnetometers \\
& Force on iron & Dynamic Switchable clamps, holding magnets \\
& Eddy currents & Metal separation, brakes \\
\bottomrule
\end{tabular}
\caption{Applications of permanent magnet materials, 
adapted from \textcite{coey2002}.}
\tablabel{magnet-applications}
\end{table}


That magnets can apply forces to one another over a distance is
quite a novel concept in a mechanical world accustomed to
friction. It has been a short while, relatively speaking, that
it has been possible to even \emph{produce} magnets with enough
coercive force to apply useful mechanical forces. Non-contact
magnetics in mechanical systems is advantageous due to high
precision and wear-free operation due to lack of friction. This
section looks broadly at some of the main applications of the
field.

\subsection{Maglev transportation}

The largest body of research into magnetic levitation is on
so-called `maglev' transportation. Its well-known goal is to
use a levitated train or car to provide extremely fast and
efficient transportation. This field, which is rather diverse
in terms of the techniques under investigation, is finally now
achieving commercial application in the real world after some
20 or 30 years of research.  While it has some concepts in
common with this research (large loads, magnets), the
techniques used tend to be rather distanced from those that
will be applied for this project because they focus on
transportation rather than \emph{elimination} of movement.


\subsection{Magnetic actuators}

In more recent years, another application for magnetic
levitation has been investigated, which is the precision
control of a levitated platform.  Commonly cited for use in
the semiconductor industry for photolithography, these
levitators were first researched around 20 years ago.

The first designs allowed travel in a single direction, \eg,
\textcite{trumper1992}, while more recent developments allow
more directions of control.  Such devices are capable of
supporting small loads, and applying horizontal translation
forces to effect displacements of up to around \SI{200}{mm}
with nanometre precision. Two planar devices are invented in
the independent theses of \textcite{kim1997} and
\textcite{molenaar2000}. Most recently, a six degree of
freedom non-contact actuator was demonstrated by
\textcite{verma2004}. See also the device built by
\textcite{kim2007} to support around \SI{2}{kg} over a travel
of $\SI{5}{mm}\times\SI{5}{mm}$ with nanometre precision. The
high performance and mechanical simplicity of their design is
note-worthy.

Here're some more to look at: \textcite{boeij2008,zhang2008a}

The reason these devices are unsuitable for this research is
due to their travelling capability. Rather than using the
primarly magnetic flux for load support, these designs use it
in order to provide positioning control in the horizontal
directions.

Here's something new: \textcite{shameli2008}.

A recent six degree of freedom actuator has been demonstrated
by \textcite{jansen2008}, which supports loads in the order of
\SI{10}{kg} with a relatively large air gap (\SI{1}{mm}--\SI{2}{mm}) 
and large stroke ($\SI{230}{mm}\times\SI{230}{mm}$).

[\textcite{dasilveira2005}] Analytical expression for the normal force
between two magnets on a back-iron plate and a perpendicular coil. The system
is for a planar actuator, and the motivation is to be able to determine the
amount of out-of-plane force generated by a particular design. Could very well
be useful for some of my ideas.

\subsection{Interesting devices}

I like magnetic levitation of objects in a wind tunnel
\cite{higuchi2008}.

Magnetic fields can be used for a vast array of scientific uses. For example,
noncontact sensing of material properties that involve variable conductivity,
including fatigue cracks, defects in printed circuit boards, and even plastic
landmine detection \cite{mukhopadhyay2005}.

Here would be a good place to cite the brain, nerve, stuff, etc
\parencite{lu2008,demachi2008}


Here's a fun application of magnetics where a computer input device is built
with magnetic sensors placed on the wrist in order to sense single finger-tip
motion from the opposite hand \parencite{han2008}.

I don't know if I care, but \textcite{vanwest2007} created a
haptic interface for manuipulating small objects with magnetic
levitation using the so-called `zero power' technique well
known due to Mizuno.

\textcite{park2008} demonstrates a MIMO controller for a flywheel energy
storage mechanism using magnetic bearings while applying active vibration
isolation.

[\textcite{tomie2005}] This paper's a bit of fun; uses a magnet attached
to a cantilever, excited by an external field in a water tank, to propel a
robotic fish. Only left-right oscillations were produced, so the fish was
constrained to move in a plane; two turning methods are investigated.




\section{Digression}

The method for literature review taken in this thesis may be considered rather
eccentric. During the course of my research, I couldn't help but notice the
flood of literature to be an almost unstoppable flow of information that was
rather difficult to remain `on top of'. Certainly required some expenditure of
effort on my part. And perhaps to my detriment, the bibliography in this
thesis is rather large — although certainly not exceeding that of a single
literature review in certain specific fields.

This thesis is a drop of water in the ocean of this literature that is
increasing every month. It will be a defining problem in the next few decades,
I believe, to attempt a unification and consolidation of the amount of
information that is currently available and, also, and more importantly, the
way that new work is published.

\section{Notation}

The mathematics in this thesis is typeset consistently but somewhat
differently than might be expected. Here's an arbitrary example:
\begin{dmath*}
f\fn{x} = \half\gp{x+\Sin{x}}.
\end{dmath*}


Here's a nice big glossary section that will take me fucking ages to get
right. Maybe I should just scrap it.

\section{Typesetting}
The typesetting of this thesis has been carefully designed with the following main objectives:
\begin{enumerate}
\item Ease of reading content, and
\item Ease of finding information.
\end{enumerate}
For the first point, a highly legible font has been chosen and the size of the
text calculated for optimal reading properties. For the second point, the
outer margins of the page have been utilised for holding `markers' such as
equation numbers and section numbers; this places such information close the
edge of the paper to aid `flicking through' the thesis. It also moves them
away from the main text where their encroachment of the material in the main
text is less useful.

In the \PDF\ version of this document, clickable hyperlinks have been inserted in
all relevant cross-referencing situations to aid navigation.

\section{Paraphrasing David Foster Wallace}

David Foster Wallace discusses the feeling of writing a book.
\note{\url{http://www.badgerinternet.com/~bobkat/jesty.html}}
His words work equally well for a thesis:

\begin{quotation}
You love [it] very much. And you want others to love it, too, when the time
finally comes for [it] to go out and face the world. But wanting other people
to love it, now, means hoping that others somehow won't see [it] as you see it
\dash as a grotesque, malformed betrayal of the very possibilities that
spawned it. You want to sort of fool people: you want them to see as perfect
what you in your heart know is a betrayal of all perfection. Or else you don't
want to fool these people; [...] You want to be terribly wrong: you want [its]
hideousness to turn out to have been nothing but your own weird delusion or
hallucination. But that'd mean you were crazy ... But worse: it'd also mean
you see and despise hideousness in a thing you made (and love), in your spawn,
in certain ways you. But that's still what you most want: to be completely,
insanely, suicidally wrong.

But it's still all a lot of fun. Don't get me wrong.
\end{quotation}
